Hard Statistics in Economics: Investigating Economic Drivers in Individual Confidence in the DOW in the US

### 2024-12-04 paper/paper.qmd
final edits

## Economic Variables Are Poor Predictors of Market Confidence
Despite spending time to choose a model with normalized errors and the smallest mean square errors based on predictions, this model still does not perform well and it's interpretation lacks good understanding from an investors standpoint. As discussed in the data section, we do not expect this model to perform perfectly given that is it attempting to predict one-year confidence indexes during the peak of COVID-19, but nonetheless we cannot conclude it has great predictive performance. Its performance indicates that these economic factors are not all good predictors of market confidence. It shows that the market is not influenced by these economic factors alone and there is a much more complex and intricate system of factors that play into how an investor may feel about the future. It would have been nice to find that the most common economic statistics, like GDP growth or the VIX, play a large role in ones confidence in the market, but there is no obvious linear relationship.

>>>>

## Economic Variables Are Poor Predictors of Market Confidence
Despite spending time to choose a model with normalized errors and the smallest mean square errors based on predictions, this model still does not perform well and it's interpretation lacks good understanding from an investors standpoint. As discussed in the end of the model section, we do not expect this model to perform perfectly given that is it attempting to predict one-year confidence indexes during the peak of COVID-19, but nonetheless we cannot conclude it has great predictive performance. Its performance indicates that these economic factors are not all good predictors of market confidence. It shows that the market is not influenced by these economic factors alone and there is a much more complex and intricate system of factors that play into how an investor may feel about the future. It would have been nice to find that the most common economic statistics, like GDP growth or the VIX, play a large role in ones confidence in the market, but there is no obvious linear relationship.
